\bf Calendar-based graphics for visualizing people's daily schedules

### 2019-04-27 main.Rmd
done with draft revision
cc @dicook can you please take a look?

Figure \@ref(fig:dow) shows the energy use across days of week in the form of letter value plots [@hofmann2017letter]. Letter value plots are a variant of boxplots for large data, with other quantiles represented by boxes. Letters indicate the fraction of the data divisions, for example, F indicates fourths or quartiles, and the two outer ends of the box are the 25th and 75th percentile, the same traditional ends of the box as a boxplot. The letter E indicates eighths, with box ends being 12.5th and 87.5th percentiles of the data. These additional boxes replace the whiskers in a traditional boxplot. The letter value plots for the households, show a line indicating the median (M) and the innermost boxes corresponding to the fourth (F) and the eighth (E) quantile divisions. Inspecting the medians across households tells us that household 3, a family size of one couple and two kids, uses more energy over the week days, than other households. The relatively larger boxes for household 2 indicates greater variability in daily energy consumption with noticeable variations on Thursdays, and much higher usage over the weekends. The other two households (1 and 4) tend to consume more energy with more  variation on the weekends relative to the week days, reflecting of work and leisure patterns.

```{r dow, fig.height = 7, fig.cap = "Letter value plots of daily energy usage against day of week for four households, with one line dislaying the median (M) and each box corresponding to the fourth (F) and eighth (E) paired quantile estimates. Suggested by the medians, household 3 uses more enery than the others on the week days, due to a large family size. By constrast, household 2 sees considerally large variability."}
```

>>>>

Figure \@ref(fig:dow) shows the energy use across days of week using boxplots. Inspecting the medians across households tells us that household 3, a family size of one couple and two kids, uses more energy over the week days, than other households. The relatively larger boxes for household 2 indicates greater variability in daily energy consumption with noticeable variations on Thursdays, and much higher usage over the weekends. The other two households (1 and 4) tend to consume more energy with more variation on the weekends relative to the week days, reflecting of work and leisure patterns.

```{r dow, fig.height = 7, fig.cap = "Boxplots of daily energy usage against day of week for four households. Suggested by the medians, household 3 uses more enery than the others on the week days, due to a large family size. By constrast, household 2 sees considerally large variability."}
```

### 2019-04-27 main.tex
done with draft revision
cc @dicook can you please take a look?

Figure \ref{fig:dow} shows the energy use across days of week in the form of letter value plots \citep{hofmann2017letter}. Letter value plots are a variant of boxplots for large data, with other quantiles represented by boxes. Letters indicate the fraction of the data divisions, for example, F indicates fourths or quartiles, and the two outer ends of the box are the 25th and 75th percentile, the same traditional ends of the box as a boxplot. The letter E indicates eighths, with box ends being 12.5th and 87.5th percentiles of the data. These additional boxes replace the whiskers in a traditional boxplot. The letter value plots for the households, show a line indicating the median (M) and the innermost boxes corresponding to the fourth (F) and the eighth (E) quantile divisions. Inspecting the medians across households tells us that household 3, a family size of one couple and two kids, uses more energy over the week days, than other households. The relatively larger boxes for household 2 indicates greater variability in daily energy consumption with noticeable variations on Thursdays, and much higher usage over the weekends. The other two households (1 and 4) tend to consume more energy with more variation on the weekends relative to the week days, reflecting of work and leisure patterns.

@@

\caption{Letter value plots of daily energy usage against day of week for four households, with one line dislaying the median (M) and each box corresponding to the fourth (F) and eighth (E) paired quantile estimates. Suggested by the medians, household 3 uses more enery than the others on the week days, due to a large family size. By constrast, household 2 sees considerally large variability.}\label{fig:dow}
\end{figure}

>>>>

Figure \ref{fig:dow} shows the energy use across days of week using boxplots. Inspecting the medians across households tells us that household 3, a family size of one couple and two kids, uses more energy over the week days, than other households. The relatively larger boxes for household 2 indicates greater variability in daily energy consumption with noticeable variations on Thursdays, and much higher usage over the weekends. The other two households (1 and 4) tend to consume more energy with more variation on the weekends relative to the week days, reflecting of work and leisure patterns.

@@

\caption{Boxplots of daily energy usage against day of week for four households. Suggested by the medians, household 3 uses more enery than the others on the week days, due to a large family size. By constrast, household 2 sees considerally large variability.}\label{fig:dow}
\end{figure}
